Restrictive Clearance Comparison

### 2025-08-01 data-raw/ClearanceProject-2-RelativeLikelihood.Rmd
updating data files

```{r kelim-questions}
# Original data, filtered for common_chems
# par_DF
this_kelim_prefit <- this_pk$prefit$par_DF %>%
  filter(
    param_name %in% "kelim",
  ) %>%
  distinct(Chemical, Species, param_name, lower_bound, upper_bound, start)

@@

# reorder the Chemical names prior to plotting
df_valcomp %>%
  mutate(Chemical = factor(
    x = Chemical,
    levels = val_hclust$labels[val_hclust$order]
  )) %>%
  pivot_longer(
    cols = A_rest:C_nonrest,
    names_to = "comparison", values_to = "logres"
  ) %>%
  mutate(
    comparison = case_when(
      comparison == "A_nonrest" ~ "free kelim vs httk nonrestrictive",
      comparison == "A_rest" ~ "free kelim vs httk restrictive",
      comparison == "B_nonrest" ~ "restrictive kelim vs httk nonrestrictive",
      comparison == "B_rest" ~ "restrictive kelim vs httk restrictive",
      comparison == "C_nonrest" ~ "nonrestrictive kelim vs httk nonrestrictive",
      comparison == "C_rest" ~ "nonrestrictive kelim vs httk restrictive",
    ),
    comparison = factor(comparison,
                        levels = c(
                          "free kelim vs httk restrictive",
                          "free kelim vs httk nonrestrictive",
                          "restrictive kelim vs httk restrictive",
                          "nonrestrictive kelim vs httk nonrestrictive",
                          "nonrestrictive kelim vs httk restrictive",
                          "restrictive kelim vs httk nonrestrictive"
                        )
    )
  ) %>%
  ggplot(aes(x = comparison, y = Chemical, fill = logres)) +
  geom_tile() +
  scale_fill_gradient2(
    mid = "grey5", high = "orange", low = "green3",
    name = "Total Clearance\nlog10-scale difference",
    limits = c(-4, 4),
    oob = scales::oob_squish
  ) +
  coord_fixed(ratio = 0.3) +
  theme_bw() +
  theme(
    axis.text.x = element_text(hjust = 1, angle = 45),
    axis.ticks.y = element_blank(),
    panel.grid = element_blank(),
    axis.title.x = element_blank()
  )

>>>>

```{r kelim-questions}
# Original data, filtered for common_chems
# par_DF
this_kelim_prefit <- this_pk$prefit$par_DF %>%
  filter(
    param_name %in% "kelim"
  ) %>%
  distinct(Chemical, Species, param_name, lower_bound, upper_bound, start)

@@

# reorder the Chemical names prior to plotting
df_valcomp %>%
  mutate(Chemical = factor(
    x = Chemical,
    levels = val_hclust$labels[val_hclust$order]
  )) %>%
  pivot_longer(
    cols = A_rest:C_nonrest,
    names_to = "comparison", values_to = "logres"
  ) %>%
  mutate(
    comparison = case_when(
      comparison == "A_nonrest" ~ "free kelim vs httk nonrestrictive",
      comparison == "A_rest" ~ "free kelim vs httk restrictive",
      comparison == "B_nonrest" ~ "restrictive kelim vs httk nonrestrictive",
      comparison == "B_rest" ~ "restrictive kelim vs httk restrictive",
      comparison == "C_nonrest" ~ "nonrestrictive kelim vs httk nonrestrictive",
      comparison == "C_rest" ~ "nonrestrictive kelim vs httk restrictive"
    ),
    comparison = factor(comparison,
                        levels = c(
                          "free kelim vs httk restrictive",
                          "free kelim vs httk nonrestrictive",
                          "restrictive kelim vs httk restrictive",
                          "nonrestrictive kelim vs httk nonrestrictive",
                          "nonrestrictive kelim vs httk restrictive",
                          "restrictive kelim vs httk nonrestrictive"
                        )
    )
  ) %>%
  ggplot(aes(x = comparison, y = Chemical, fill = logres)) +
  geom_tile() +
  scale_fill_gradient2(
    mid = "grey5", high = "orange", low = "green3",
    name = "Total Clearance\nlog10-scale difference",
    limits = c(-4, 4),
    oob = scales::oob_squish
  ) +
  coord_fixed(ratio = 0.3) +
  theme_bw() +
  theme(
    axis.text.x = element_text(hjust = 1, angle = 45),
    axis.ticks.y = element_blank(),
    panel.grid = element_blank(),
    axis.title.x = element_blank()
  )
